---
title: " P8105 Homework 5"
author: "aw3253"
date: "11/20/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(p8105.datasets)
```

# Problem 1

Describe Raw Data:

```{r message=FALSE}
homicide_df=
  read_csv("./data/homicide-data.csv", na=c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city,state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )
  ) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```


Now focus on Baltimore, MD 

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test =
prop.test(
    x = baltimore_summary %>% pull(unsolved),
    n = baltimore_summary %>%  pull(n))

baltimore_test %>% 
  broom::tidy()
```

Iteration across cities

```{r}
prop_test_function = function(city_df) {
  
  city_summary = 
      city_df %>% 
      summarize(
        unsolved = sum(resolution == "unsolved"),
        n = n()
      )
  city_test =
      prop.test(
        x = city_summary %>% pull(unsolved),
        n = city_summary %>%  pull(n))
  
  return(city_test)
  
}
prop_test_function(baltimore_df)
homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()
```

Iteration across all cities

```{r}
results_df =
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>%  
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

Plot showing estimates and confidence intervals 

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x=city_state, y=estimate)) + 
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

## Problem 2

A dataframe containing all file names:

```{r}
file_names_df = 
  files = tibble(list.files("./data/zip_data/"))


file_names_df
```


Iteration over file names:

```{r}
loop_files = function(x) {
  
  data = 
    read_csv(paste0("./data/zip_data/",x)) %>% 
    mutate(file_names = x)
  
}

all_data = map_df(file_names_df, loop_files)
```


Tidying Data:

```{r}
new_data = 
  all_data %>% 
  gather(key=week, value = arm_val, week_1:week_8)%>% 
   separate(
    col = file_names,
    into= c("arm","id"),
    sep = "_"
           )  %>% 
  mutate(
    arm = recode(
      arm,
      "con" = "control",
      "exp" = "experimental"
    ),
    id=substr(id,start=1, stop=2), 
  ) 

new_data
```


Spaghetti Plot

```{r}
tidy_plot =
ggplot(
  data = new_data, aes(x=week, y=arm_val, group=id))+
  geom_line(aes(color=id)) + 
  geom_point(size=0.5) + 
  facet_grid(. ~ arm) +
  labs(
    title= "Observations over Time by Study Arm",
      x= "Week",
      y= "Arm Values"
    )

tidy_plot
```

For subjects in the experimental arm, the values increased over time but for the controls, the values don't have a distinct trend over time. While the max arm values for controls is less than 5.0 units, it is much higher for the experimental subjects. 

